Effort and Delay Discounting in a Foraging Environment

### 2019-05-07 Cost2/Cost2_prereg_remake.Rmd
section 16.1 of cost 2 preregistration ready

# Around 10% seemed to have been influenced by previous quitting
propAR_effects <- mean(AR_CIs) * 100
```

To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero. By this measure, around `r round(propAR_effects)` percent of our participants seemed to have been influenced by recent quitting. However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.

@@

``` {r 16.1.3. Earnings, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# Pairwise comparison
# earningsPerm <- permute(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog]) # I believe this more
# earningsRsq <- cohenD(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog])

# linear model (think of doing a Poisson Regression instead, since earnings are not normally distributed [although bootstrapped they're fine])
propAllsq <- summaryData$propComplete^2 
lmEarn <- lm(Earnings ~ propComplete + propAllsq, data = summaryData)
summaryEarn <- summary(lmEarn)
coeffsEarn <- lmEarn$coefficients
summaryData$tempLine <- seq(0,1,length=totalSubs) # for plotting
summaryData$earnFitLine <- coeffsEarn[1] + coeffsEarn[2]*summaryData$tempLine + coeffsEarn[3]*(summaryData$tempLine^2)

# plotting
# boxplot(summaryData$Earnings[indxWait],
#         summaryData$Earnings[indxCog],
#         summaryData$Earnings[indxPhys],
#         summaryData$Earnings[indxEasy],
#         names = lbls,
#         main = "Total Earnings for Each Group",
#         ylab = "Total Earnings (pts)",
#         xlab = "Group",
#         col = cols)
# earnBoxplot <- ggplot(data = summaryData, aes(Group, Earnings, fill = Group)) +
#         geom_boxplot(show.legend = F) +
#         scale_fill_manual(values = cols) +
#         labs(title = "Total Earned per Group", y = "Total Earnings (Cents)", x = "") +
#         theme_classic()

# earnings (inverse-U, which makes sense because either over or under accepting are detrimental to earnings)
# plot(summaryData$propComplete[indxWait],
#      summaryData$Earnings[indxWait],
#      main = "Total Earnings as a Function of Proportion Accepted",
#      xlab = "Total Proportion Completed",
#      ylab = "Total Earned",
#      col=cols[1],
#      xlim=c(0.2,1),
#      ylim = c(1000,2000),
#      pch=16,
#      cex = lthick - 0.5)
# points(summaryData$propComplete[indxCog],
#        summaryData$Earnings[indxCog],
#        col=cols[2],
#        pch=16,
#        cex = lthick - 0.5)
# points(summaryData$propComplete[indxPhys],
#        summaryData$Earnings[indxPhys],
#        col=cols[3],
#        pch=16,
#        cex = lthick - 0.5)
# points(summaryData$propComplete[indxEasy],
#        summaryData$Earnings[indxEasy],
#        col=cols[4],
#        pch=16,
#        cex = lthick - 0.5)
# legend("topright",
#        lbls,
#        fill = cols,
#        cex = 0.8)
# lines(x, coeffsEarn[1] + coeffsEarn[2]*x + coeffsEarn[3]*(x^2),
#        col="black",
#       lwd = lthick)

earnFitplot <- ggplot(data = summaryData, aes(propComplete, Earnings)) + 
         geom_point(aes(color = Group), size = 2, show.legend = F) + 
         geom_line(aes(tempLine, earnFitLine), size = 1.5, alpha = 0.7) +
         scale_color_manual(values = cols) + 
         xlim(0.2,1) +
         labs(title = "Earnings as a Function of Acceptances", x = "Proportion Accepted", y = "") +
         theme_classic()

earnFitplot

@@

  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances-either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.). This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*

``` {r 16.1.4., echo=FALSE}
# Split the data frame into every combination of parameters of interest
splitData <- split(allProp2, list(allProp2$Reward, allProp2$Handling, allProp2$Group))

# Perform a paired t-test on every combination of parameters
# Given that 20 cent rewards demand constant acceptances, we expect the proportions to be constant for these choices
# This gives an error in the t.test due to the lack of variability and normal errors, so we use try to bypass this issue
splitData_tests <- sapply(splitData, function(data) try(t.test(data$propComplete, mu = unique(data$Optimal))$p.value))

# Adjust for multiple comparisons using BY-FDR
trueProp$Deviation_pval <- round(p.adjust(splitData_tests, method = "BY"), digits = 2)
trueProp$Deviation_pval[is.na(trueProp$Deviation_pval)] <- 1
# trueProp[trueProp$Deviation_pval < 0.05, ]

# Proportion of significant deviations from optimality
splitData_prop <- round(sum(trueProp$Deviation_pval < 0.05, na.rm = T) / 36, digits = 2)
```

>>>>

# Around 10% seemed to have been influenced by previous quitting
prcntAR_effects <- mean(AR_CIs) * 100
```

To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero. By this measure, around `r round(prcntAR_effects)` percent of our participants seemed to have been influenced by recent quitting. However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.

@@

``` {r 16.1.3. Earnings, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Cost) %>%
  summarise(Earnings = sum(Reward[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

# linear fit of earnings x prop accept
lmEarn <- lm(Earnings ~ pComplete + pComplete2, data = temp)

# plot
(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = cols) + 
         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Accepted", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = cols) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16)))

@@

  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.). This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*

``` {r 16.1.4., echo=FALSE}
# in order
# clean data, 
# calculate each individual's prop. accept,
# calculate t.tests with optimality as null mean,
# correct pvalues with FDR
temp <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID, Handling, Reward, Cost) %>%
  summarise(pComplete = mean(Choice)) %>%
  mutate(optimal = case_when(
          (Handling == 10 & Reward < 8) ~ 0,
          (Handling == 14 & Reward < 20) ~ 0,
          TRUE ~ 1
        )) %>% 
  group_by(Handling, Reward, Cost) %>%
  summarise(meanAccept = mean(pComplete),
            sdAccept = sd(pComplete),
            optimal = unique(optimal),
            pvals = tryCatch(t.test(pComplete, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
  mutate(FDR = p.adjust(pvals, method = "BY"),
         significant = FDR < 0.05)

# proportion of significant ones
# eventually find a way to plot this
splitData_prop <- mean(temp$significant, na.rm = T)
```
